Data_visualization

### 2018-08-07 Rmd/Data_visualization.Rmd
last changes

#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

@@

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")

@@

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"

#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Different colour per family
b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomea purpurea",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

>>>>

brol_seed_set_brassicaceae <- filter(brol_seed_set_final, Family %in% c("Brassicaceae"))
brol_seed_set_convolvulaceae <- filter(brol_seed_set_final, Family %in% c("Convolvulaceae"))
brol_seed_set_solanaceae <- filter(brol_seed_set_final, Family %in% c("Solanaceae"))
brol_seed_set_final$Family[is.na(brol_seed_set_final$Family)] <- "Solanum lycopersicum"

brol_seed_set_cross=brol_seed_set_cross[,-c(5,6)]
brol_seed_set_cross$Family <- "other"
brol_seed_set_self=brol_seed_set_self[,-c(5,6)]
brol_seed_set_self$Family <- "other"
brol_seed_set_control=brol_seed_set_control[,-c(5,6)]
brol_seed_set_control$Family <- "other"
brol_seed_set_flower=brol_seed_set_flower[,-c(5,6)]
brol_seed_set_flower$Family <- "other"

brol_seed_set_final=rbind(brol_seed_set_brassicaceae, brol_seed_set_convolvulaceae, 
                          brol_seed_set_solanaceae, brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
                          brol_seed_set_flower)
#Different colour per family
a <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

brra_seed_set_brassicaceae <- filter(brra_seed_set_final, Family %in% c("Brassicaceae"))
brra_seed_set_convolvulaceae <- filter(brra_seed_set_final, Family %in% c("Convolvulaceae"))
brra_seed_set_solanaceae <- filter(brra_seed_set_final, Family %in% c("Solanaceae"))
brra_seed_set_final$Family[is.na(brra_seed_set_final$Family)] <- "Solanum lycopersicum"

brra_seed_set_cross=brra_seed_set_cross[,-c(5,6)]
brra_seed_set_cross$Family <- "other"
brra_seed_set_self=brra_seed_set_self[,-c(5,6)]
brra_seed_set_self$Family <- "other"
brra_seed_set_control=brra_seed_set_control[,-c(5,6)]
brra_seed_set_control$Family <- "other"
brra_seed_set_flower=brra_seed_set_flower[,-c(5,6)]
brra_seed_set_flower$Family <- "other"

brra_seed_set_final=rbind(brra_seed_set_brassicaceae, brra_seed_set_convolvulaceae, 
                          brra_seed_set_solanaceae, brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
                          brra_seed_set_flower)

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ersa_seed_set_brassicaceae <- filter(ersa_seed_set_final, Family %in% c("Brassicaceae"))
ersa_seed_set_convolvulaceae <- filter(ersa_seed_set_final, Family %in% c("Convolvulaceae"))
ersa_seed_set_solanaceae <- filter(ersa_seed_set_final, Family %in% c("Solanaceae"))
ersa_seed_set_final$Family[is.na(ersa_seed_set_final$Family)] <- "Solanum lycopersicum"

ersa_seed_set_cross=ersa_seed_set_cross[,-c(5,6)]
ersa_seed_set_cross$Family <- "other"
ersa_seed_set_self=ersa_seed_set_self[,-c(5,6)]
ersa_seed_set_self$Family <- "other"
ersa_seed_set_control=ersa_seed_set_control[,-c(5,6)]
ersa_seed_set_control$Family <- "other"
ersa_seed_set_flower=ersa_seed_set_flower[,-c(5,6)]
ersa_seed_set_flower$Family <- "other"

ersa_seed_set_final=rbind(ersa_seed_set_brassicaceae, ersa_seed_set_convolvulaceae, 
                          ersa_seed_set_solanaceae, ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
                          ersa_seed_set_flower)

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

##
###
#S. ALBA  
###
##
#

@@

sial_seed_set_brassicaceae <- filter(sial_seed_set_final, Family %in% c("Brassicaceae"))
sial_seed_set_convolvulaceae <- filter(sial_seed_set_final, Family %in% c("Convolvulaceae"))
sial_seed_set_solanaceae <- filter(sial_seed_set_final, Family %in% c("Solanaceae"))
sial_seed_set_final$Family[is.na(sial_seed_set_final$Family)] <- "Solanum lycopersicum"

sial_seed_set_cross=sial_seed_set_cross[,-c(5,6)]
sial_seed_set_cross$Family <- "other"
sial_seed_set_self=sial_seed_set_self[,-c(5,6)]
sial_seed_set_self$Family <- "other"
sial_seed_set_control=sial_seed_set_control[,-c(5,6)]
sial_seed_set_control$Family <- "other"
sial_seed_set_flower=sial_seed_set_flower[,-c(5,6)]
sial_seed_set_flower$Family <- "other"

sial_seed_set_final=rbind(sial_seed_set_brassicaceae, sial_seed_set_convolvulaceae, 
                          sial_seed_set_solanaceae, sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
                          sial_seed_set_flower)

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ipaq_seed_set_brassicaceae <- filter(ipaq_seed_set_final, Family %in% c("Brassicaceae"))
ipaq_seed_set_convolvulaceae <- filter(ipaq_seed_set_final, Family %in% c("Convolvulaceae"))
ipaq_seed_set_solanaceae <- filter(ipaq_seed_set_final, Family %in% c("Solanaceae"))
ipaq_seed_set_final$Family[is.na(ipaq_seed_set_final$Family)] <- "Solanum lycopersicum"

ipaq_seed_set_cross=ipaq_seed_set_cross[,-c(5,6)]
ipaq_seed_set_cross$Family <- "other"
ipaq_seed_set_self=ipaq_seed_set_self[,-c(5,6)]
ipaq_seed_set_self$Family <- "other"
ipaq_seed_set_control=ipaq_seed_set_control[,-c(5,6)]
ipaq_seed_set_control$Family <- "other"
ipaq_seed_set_flower=ipaq_seed_set_flower[,-c(5,6)]
ipaq_seed_set_flower$Family <- "other"

ipaq_seed_set_final=rbind(ipaq_seed_set_brassicaceae, ipaq_seed_set_convolvulaceae, 
                          ipaq_seed_set_solanaceae, ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
                          ipaq_seed_set_flower)

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomoea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ippu_seed_set_brassicaceae <- filter(ippu_seed_set_final, Family %in% c("Brassicaceae"))
ippu_seed_set_convolvulaceae <- filter(ippu_seed_set_final, Family %in% c("Convolvulaceae"))
ippu_seed_set_solanaceae <- filter(ippu_seed_set_final, Family %in% c("Solanaceae"))
ippu_seed_set_final$Family[is.na(ippu_seed_set_final$Family)] <- "Solanum lycopersicum"

ippu_seed_set_cross=ippu_seed_set_cross[,-c(5,6)]
ippu_seed_set_cross$Family <- "other"
ippu_seed_set_self=ippu_seed_set_self[,-c(5,6)]
ippu_seed_set_self$Family <- "other"
ippu_seed_set_control=ippu_seed_set_control[,-c(5,6)]
ippu_seed_set_control$Family <- "other"
ippu_seed_set_flower=ippu_seed_set_flower[,-c(5,6)]
ippu_seed_set_flower$Family <- "other"

ippu_seed_set_final=rbind(ippu_seed_set_brassicaceae, ippu_seed_set_convolvulaceae, 
                          ippu_seed_set_solanaceae, ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
                          ippu_seed_set_flower)
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"

#Different colour per family
b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomoea purpurea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
